Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-14 krs-survey.tex
Section on memory

>>>>

Memory has been studied at lenght in the cognitive neuroscience community, and
the ability to forget is proven to play a key role for the cognition.
\fxwarning{Add references -> ask Claire or Gladys}.

Most knowledge representation systems offers some kind of working memory as a
pool of facts that are not forgotten by the robot until it is halted. Some
systems may propose persistent storages that allow the robot knowledge to grow
over time, while other may offer a larger range of memory categories, like
short term memory (that last for a couple of seconds) or episodic memory (that
allows the robot to selectively remember facts associated to specific events).
\fxwarning{Add references of paper in the robotics community that have
explicitely tackled the memory issue}.
